\documentclass[11pt, letterpaper, oneside]{article}

\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{color}
\usepackage{baskervald}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{hyperref}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

\pagestyle{empty}

% Name and contact information
\newcommand{\name}{Corey Wu}
\newcommand{\program}{3A Computer Engineering}
\newcommand{\website}{http://www.coreywu.com}
\newcommand{\github}{\href{https://github.com/coreywu}{github.com/coreywu}}
\newcommand{\phone}{(647) 502-9912}
\newcommand{\email}{c69wu@uwaterloo.ca}

% A horizontal rule for sections
\newcommand{\HRule}[2]{\textcolor{#1}{\rule{\linewidth}{#2}}}
 
% A section tile command
\newcommand{\sectiontitle}[1]{\begin{minipage}{\textwidth}\vspace{-7.5pt}\begin{flushleft}\hspace{-20.5pt}\vspace{-25pt}
\Large\MakeUppercase{#1}\end{flushleft}\end{minipage}\\\HRule{black}{0.15mm}\vspace{\baselineskip}}

% An environment for a resume section
\newenvironment{ressection}[1]{
  \sectiontitle{#1}}
  {\vspace{-\baselineskip}}
  
% Resentry defines a position
% Arg1: Position title
% Arg2: Company or Office---Company
% Arg3: Location, PROV
% Arg4: Date Range
\newcommand{\resentryheader}[4]{
    \vspace{-6pt}
    \textbf{#1}\hspace{\stretch{1}}\textcolor{black}{#3}\\
    \textit{#2}\hspace{\stretch{1}}\textcolor{black}{#4}\\
}
 
% A resitem is a simple list element
\newcommand{\resitem}[1]{
    \vspace{2pt}
    \item \begin{flushleft} #1 \end{flushleft}
}

\newcommand{\resinneritem}[1]{
	\vspace{-5pt}
    \item \begin{flushleft} #1 \end{flushleft}
}

\newcommand{\resskillsitem}[2]{
	\vspace{-12pt}
    \item \begin{flushleft} \textbf{#1}: #2 \end{flushleft}
    \vspace{4pt}
}

\newcommand{\resawardentry}[3]{
  \begin{minipage}{6.3in}
  \hspace{-24pt}\textbf{#1},
  {#2}\hfill\textcolor{black}{#3}\\
  \vspace{-5pt}
  \vspace{0.5\baselineskip}
  \end{minipage}
}

\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% This is a resume entry with a header and bullet items
\newenvironment{resentry}[4]{
  \begin{minipage}{\textwidth}
  \vspace{-3pt}
    \resentryheader{#1}{#2}{#3}{#4}
        \vspace{-\baselineskip}
    \begin{itemize}[noitemsep,nolistsep]
}{
    \end{itemize}
        \vspace{\baselineskip}
        \end{minipage}
}

\begin{document}
\begin{center}
	{\Huge \textbf{\name}}

	\ \ {\Large{\program}} \\
	\ \ \github \ \textbullet \ \email \ \
\end{center}

\vspace{-20pt}

\begin{ressection}{Skills Summary}
\begin{resentry}{Languages:}{}{}{}{}
\vspace{-16pt}
\resitem{\textbf{Experienced with:} Java, Python \ \ \ \ \textbullet \ \textbf{Familiar with:} C, \CPP, C\#, Assembly, JavaScript, PHP, Bash, VHDL}
\vspace{-10pt}
\end{resentry}
\textbf{Technologies:} PostgreSQL, MySQL, SQLite, Amazon EC2, Vagrant, VirtualBox,  \LaTeX
\\
\textbf{Tools:} Git, Eclipse, Android Studio, Vim
\end{ressection}
\vspace{14pt}

\begin{ressection}{Experience}
  \begin{resentry}{\href{http://pos.toasttab.com/}{Toast Inc.}}{Software Engineer Intern}{Boston, MA}{Aug. 2014 -- Dec. 2014}
    \resitem{Developed features and bug fixes for Android app and Java Play webserver.}
    \resitem{Designed and implemented data models and JSON serializing/deserializing logic for new Customer Relationship Management component; wrote scripts for database migrations. }
    \vspace{4pt} \hspace{-15pt}
    \textbf{Key Technologies:} Java, Android, PostgreSQL, Play Framework, JavaScript, Heroku, Hibernate.
  \end{resentry}  
  \begin{resentry}{\href{http://www.seeq.com/}{Seeq}}{Software Engineer Intern}{Seattle, WA}{Jan. 2014 -- Apr. 2014}
    \resitem{Implemented features for monitoring and configuration of server application. }
    \resitem{Developed cloud-based test architecture to perform tests on Amazon EC2 VMs using Vagrant.}
    \resitem{Worked with graph databases (Titan \& Neo4j) and big data technology.}
    \vspace{4pt} \hspace{-15pt}
    \textbf{Key Technologies:} Java, Titan, Vagrant, Amazon EC2, Python.
  \end{resentry}
  \begin{resentry}{\href{http://polar.me/}{Polar}}{Test Automation Developer}{Toronto, ON}{Apr. 2013 -- Aug. 2013}
    \resitem{Helped team achieve continuous deployment using Buildbot, significantly reducing release cycle time.}
    \vspace{4pt} \hspace{-15pt}
    \textbf{Key Technologies:} Java, JUnit, Eclipse, Selenium, Buildbot.
  \end{resentry}
\end{ressection}

\begin{ressection}{Projects}
  \begin{resentry}{\href{https://github.com/shamak/HTN_Scheduler}{Calendr}}{Event Scheduling Android App}{}{Oct. 2014 -- Present}
    \resitem{Created an event scheduling Android app using Google Calendar and Contact APIs.}
    \resitem{Implemented algorithm for selecting optimal event times based on participants' schedules.}
    \vspace{4pt} \hspace{-15pt}
    \textbf{Key Technologies:} Java, Android, PHP, MySQL.
  \end{resentry}
  \begin{resentry}{\href{https://github.com/coreywu/Connect4}{Embedded Connect 4 Game}}{Connect 4 with AI on a Microcontroller}{}{Nov. 2014 -- Present}
    \resitem{Built on a TI TM4C123 Microcontroller with output to an LCD display. }
    \resitem{Implemented minimax algorithm with alpha-beta pruning for intelligent AI.}
    \vspace{4pt} \hspace{-15pt}
    \textbf{Key Technologies:} C, Python.
  \end{resentry}
  \begin{resentry}{\href{https://play.google.com/store/apps/details?id=ca.uwaterloo.uwfoodservices&hl=en}{UW Food Menu}}{Waterloo Food Services Android App}{}{Jun. 2013 -- Aug. 2013}
    \resitem{Designed an Android app which displays food services data from the University of Waterloo API.}
    \resitem{Implemented caching of data on device and integrated with Google Maps API.}
    \vspace{4pt} \hspace{-15pt}
    \textbf{Key Technologies:} Java, Android, Python, PHP, MySQL.
  \end{resentry}
  \textbf{Relevant Courses:} Algorithms \& Data Structures, Compilers, Operating Systems, Embedded Systems
\end{ressection}



\end{document}