\documentclass[11pt, letterpaper, oneside]{article}

\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{color}
\usepackage{baskervald}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{hyperref}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.5in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.5in}

\pagestyle{empty}

% Name and contact information
\newcommand{\name}{Corey Wu}
\newcommand{\program}{3B Computer Engineering}
\newcommand{\website}{http://www.coreywu.com}
\newcommand{\github}{\href{https://github.com/coreywu}{github.com/coreywu}}
\newcommand{\phone}{(647) 502-9912}
\newcommand{\email}{c69wu@uwaterloo.ca}

% A horizontal rule for sections
\newcommand{\HRule}[2]{\textcolor{#1}{\rule{\linewidth}{#2}}}
 
% A section tile command
\newcommand{\sectiontitle}[1]{\begin{minipage}{\textwidth}\vspace{-7.5pt}\begin{flushleft}\hspace{-20.5pt}\vspace{-25pt}
\Large\MakeUppercase{#1}\end{flushleft}\end{minipage}\\\HRule{black}{0.15mm}\vspace{\baselineskip}}

% An environment for a resume section
\newenvironment{ressection}[1]{
  \sectiontitle{#1}}
  {\vspace{-\baselineskip}}
  
% Resentry defines a position
% Arg1: Position title
% Arg2: Company or Office---Company
% Arg3: Location, PROV
% Arg4: Date Range
\newcommand{\resentryheader}[4]{
    \vspace{-6pt}
    \textbf{#1}\hspace{\stretch{1}}\textcolor{black}{#3}\\
    \textit{#2}\hspace{\stretch{1}}\textcolor{black}{#4}\\
}

\newcommand{\resprojentryheader}[2]{
    \vspace{-6pt}
    \textbf{#1}\hspace{\stretch{1}}\textcolor{black}{#2}\\
}
 
% A resitem is a simple list element
\newcommand{\resitem}[1]{
    \vspace{2pt}
    \item \begin{flushleft} #1 \end{flushleft}
}

\newcommand{\resinneritem}[1]{
	\vspace{-5pt}
    \item \begin{flushleft} #1 \end{flushleft}
}

\newcommand{\resskillsitem}[2]{
	\vspace{-12pt}
    \item \begin{flushleft} \textbf{#1}: #2 \end{flushleft}
    \vspace{4pt}
}

\newcommand{\resawardentry}[3]{
  \begin{minipage}{6.3in}
  \hspace{-24pt}\textbf{#1},
  {#2}\hfill\textcolor{black}{#3}\\
  \vspace{-5pt}
  \vspace{0.5\baselineskip}
  \end{minipage}
}

\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% This is a resume entry with a header and bullet items
\newenvironment{resentry}[4]{
  \begin{minipage}{\textwidth}
  \vspace{-3pt}
    \resentryheader{#1}{#2}{#3}{#4}
        \vspace{-\baselineskip}
    \begin{itemize}[noitemsep,nolistsep]
}{
    \end{itemize}
        \vspace{\baselineskip}
        \end{minipage}
}

% This is a project entry with a header and bullet items
\newenvironment{resprojentry}[2]{
  \begin{minipage}{\textwidth}
  \vspace{-3pt}
    \resprojentryheader{#1}{#2}
        \vspace{-\baselineskip}
     \vspace{-2pt}
    \begin{itemize}[noitemsep,nolistsep]
}{
    \end{itemize}
        \vspace{\baselineskip}
        \end{minipage}
}

\begin{document}
\begin{center}

	{\Huge \textbf{\name}}

	\ \ {\Large{\program}} \\
	\ \ \github \ \textbullet \ \email \ \
\end{center}

\vspace{-10pt}

\begin{ressection}{Skills Summary}
  \begin{resentry}{{Languages:}}{}{}{}
	\vspace{-15pt}    
    \resitem{\textbf{Experienced with:} Java, Scala, Python}
    \vspace{-2pt}
    \resitem{\textbf{Familiar with:} C, \CPP, C\#, ARM Assembly, JavaScript, PHP, Bash, VHDL}
    \vspace{-10pt}   
  \end{resentry}  
  \hspace{-20pt} \textbf{Technologies:} Apache Solr, Apache Spark, Android, ANTLR,  PostgreSQL, MySQL, Amazon EC2, Vagrant
\end{ressection}

\vspace{20pt}

\begin{ressection}{Experience}
  \begin{resentry}{\href{http://www.bloomberg.com/professional/}{Bloomberg L.P.}}{Software Engineering}{New York City, NY}{May. 2015 -- Aug. 2015}
    \resitem{Designed and built domain specific language component of distributed Solr analytics project using ANTLR; created a generic, extensible DSL framework to build parsers for DSLs with functional syntax.}
    \resitem{Implemented parser and executor to run Spark operations for analytics on Solr documents.}
    \vspace{3pt} \hspace{-15pt}
    \textbf{Key Technologies:} Apache Solr, Apache Spark, ANTLR, Jetty.
    \vspace{6pt} 
  \end{resentry}  
  \begin{resentry}{\href{http://pos.toasttab.com/}{Toast Inc.}}{Software Engineer Intern}{Boston, MA}{Aug. 2014 -- Dec. 2014}
   \resitem{Designed and implemented data models and JSON serialization/deserialization logic for new Customer Relationship Management component; wrote scripts for database migrations. }
    \resitem{Developed features and bug fixes for Android application and Java Play webserver.}
    \vspace{3pt}  \hspace{-15pt}
    \textbf{Key Technologies:} Android, PostgreSQL, Play Framework, JavaScript, Heroku, Hibernate.
	\vspace{6pt}   
  \end{resentry}  
  \begin{resentry}{\href{http://www.seeq.com/}{Seeq}}{Software Developer Intern}{Seattle, WA}{Jan. 2014 -- Apr. 2014}
    \resitem{Developed cloud-based integration test architecture to automatically spin up VMs and execute tests on.}
    \resitem{Implemented features for monitoring and configuration of server application}
    \resitem{Worked with graph databases (Titan \& Neo4j) and researched Big Data technology.}
    \vspace{3pt} \hspace{-15pt}
    \textbf{Key Technologies:} Titan, Vagrant, Amazon EC2, Python.
	\vspace{6pt}   
  \end{resentry}
\end{ressection}

\vspace{4pt}

\begin{ressection}{Projects}
  \begin{resprojentry}{\href{https://github.com/coreywu/Connect4}{Embedded Connect4 Game}}{}
    \resitem{Built Connect 4 game with AI on TI TM4C123 Microcontroller with LCD graphics display.}
    \resitem{Implemented minimax algorithm with alpha-beta pruning for fast and intelligent AI.}
    \hspace{-15pt}
  \end{resprojentry}
  \begin{resprojentry}{\href{https://play.google.com/store/apps/details?id=ca.uwaterloo.uwfoodservices&hl=en}{UW Food Menu}}{}
    \resitem{Designed an Android application which displays food services data from the University of Waterloo API.}
    \resitem{Implemented caching of data on device and integrated with Google Maps API.}
    \vspace{2pt} \hspace{-15pt}
  \end{resprojentry}
  \begin{resprojentry}{\href{https://github.com/coreywu/CoopStatsDataAnalysis}{UW Co-op Data Analysis}}{}
    \resitem{Analysis of UW co-op data using Apache Spark.}
    \resitem{Implemented graph algorithms such as PageRank and Connected Components.}
    \vspace{2pt} \hspace{-15pt}
    \vspace{-10pt}
  \end{resprojentry}
  \vspace{-10pt}
  \textbf{Relevant Courses:} Algorithms \& Data Structures, Compilers, Operating Systems, Computer Networks, Databases
\end{ressection}
\end{document}