\documentclass[11pt, letterpaper, oneside]{article}

\usepackage{geometry}
\usepackage[T1]{fontenc}
\usepackage[dvipsnames]{color}
\usepackage{baskervald}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage{hyperref}

%-----------------------------------------------------------
%Margin setup

\setlength{\voffset}{0.1in}
\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\textheight}{11in}
\setlength{\textheight}{9.5in}
\setlength{\topmargin}{-0.25in}
\setlength{\textwidth}{7in}
\setlength{\topskip}{0in}
\setlength{\oddsidemargin}{-0.25in}
\setlength{\evensidemargin}{-0.25in}

\pagestyle{empty}

% Name and contact information
\newcommand{\name}{Corey Wu}
\newcommand{\program}{2B Computer Engineering}
\newcommand{\website}{http://www.coreywu.com}
\newcommand{\github}{\href{https://github.com/coreywu}{github.com/coreywu}}
\newcommand{\phone}{(647) 502-9912}
\newcommand{\email}{c69wu@uwaterloo.ca}

% A horizontal rule for sections
\newcommand{\HRule}[2]{\textcolor{#1}{\rule{\linewidth}{#2}}}
 
% A section tile command
\newcommand{\sectiontitle}[1]{\begin{minipage}{\textwidth}\vspace{-7.5pt}\begin{flushleft}\hspace{-20.5pt}\vspace{-25pt}
\Large\MakeUppercase{#1}\end{flushleft}\end{minipage}\\\HRule{black}{0.15mm}\vspace{\baselineskip}}

% An environment for a resume section
\newenvironment{ressection}[1]{
  \sectiontitle{#1}}
  {\vspace{-\baselineskip}}
  
% Resentry defines a position
% Arg1: Position title
% Arg2: Company or Office---Company
% Arg3: Location, PROV
% Arg4: Date Range
\newcommand{\resentryheader}[4]{
    \vspace{-6pt}
    \textbf{#1}\hspace{\stretch{1}}\textcolor{black}{#3}\\
    \textit{#2}\hspace{\stretch{1}}\textcolor{black}{#4}\\
}
 
% A resitem is a simple list element
\newcommand{\resitem}[1]{
    \vspace{2pt}
    \item \begin{flushleft} #1 \end{flushleft}
}

\newcommand{\resinneritem}[1]{
	\vspace{-5pt}
    \item \begin{flushleft} #1 \end{flushleft}
}

\newcommand{\resskillsitem}[2]{
	\vspace{-12pt}
    \item \begin{flushleft} \textbf{#1}: #2 \end{flushleft}
    \vspace{4pt}
}

\newcommand{\resawardentry}[3]{
  \begin{minipage}{6.3in}
  \hspace{-24pt}\textbf{#1},
  {#2}\hfill\textcolor{black}{#3}\\
  \vspace{-5pt}
  \vspace{0.5\baselineskip}
  \end{minipage}
}

\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% This is a resume entry with a header and bullet items
\newenvironment{resentry}[4]{
  \begin{minipage}{\textwidth}
  \vspace{-3pt}
    \resentryheader{#1}{#2}{#3}{#4}
        \vspace{-\baselineskip}
    \begin{itemize}[noitemsep,nolistsep]
}{
    \end{itemize}
        \vspace{\baselineskip}
        \end{minipage}
}

\begin{document}
\begin{center}
	{\Huge \textbf{\name}}

	\ \ {\Large{\program}} \\
	\ \ \github \ \textbullet \ \email \ \
\end{center}

\vspace{-20pt}

\begin{ressection}{Skills Summary}
\begin{resentry}{Languages:}{}{}{}{}
\vspace{-16pt}
\resitem{\textbf{Experienced with:} Java, Python \ \ \ \ \textbullet \ \textbf{Familiar with:} C, \CPP, C\#, Assembly, PHP, Bash, MATLAB}
\vspace{-10pt}
\end{resentry}
\textbf{Tools \& Technologies:} Eclipse, Android, JUnit, Vagrant, Amazon EC2, Git, Vim, MySQL, \LaTeX
\end{ressection}
\vspace{14pt}

\begin{ressection}{Experience}
  \begin{resentry}{Software Intern}{\href{http://www.seeq.com/}{Seeq Inc.}}{Hood River, OR}{Jan. 2014 -- Apr. 2014}
    \resitem{Gained experience with graph databases and big data technology.}
    \resitem{Developed a cloud-based integration test architecture to perform tests on virtual machines using Vagrant and Amazon EC2 instances.}
    \resitem{Developed a process supervisor to start component processes and integrate them into a product. }
    \vspace{4pt} \hspace{-15pt}
    \textbf{Key Technologies:} Java, Cassandra, Titan, Vagrant, Amazon EC2, Python.
  \end{resentry}
  \begin{resentry}{Test Automation Developer}{\href{http://polar.me/}{Polar} (formerly Polar Mobile)}{Toronto, ON}{Apr. 2013 -- Aug. 2013}
    \resitem{Helped team achieve continuous deployment through continuous integration using Buildbot, reducing release cycle time significantly.}
    \resitem{Developed and executed Selenium test cases in Java using the JUnit framework to thoroughly test mobile and web applications in multiple browsers.}
    \vspace{4pt} \hspace{-15pt}
    \textbf{Key Technologies:} Java, JUnit, Eclipse, Selenium, Buildbot.
  \end{resentry}
\end{ressection}

\begin{ressection}{Projects}
  \begin{resentry}{\href{https://play.google.com/store/apps/details?id=ca.uwaterloo.uwfoodservices&hl=en}{UW Food Menu}}{Waterloo Food Services Android App}{}{Mar. 2013 -- Present}
    \resitem{Designed a parser to asynchronously request and parse JSON from the University of Waterloo API and display in app; data is fetched weekly and cached for future use.}
    \resitem{Integrated with Google Maps API to display a map of eateries.}
    \resitem{Implemented Python and PHP scripts to parse API data and store in a MySQL or SQLite database.}
    \vspace{4pt} \hspace{-15pt}
    \textbf{Key Technologies:} Java, Android, Eclipse, Python, PHP, MySQL, Git.
  \end{resentry}
\end{ressection}

\begin{ressection}{Education}
  \begin{resentry}{Candidate for Bachelor of Applied Science}{University of Waterloo}{Waterloo, ON}{Sept. 2012 -- Present}
    \resitem{\textbf{Relevant Projects}}
	\textbf{\hspace{5pt}Map Navigation Android App}   
    \begin{itemize}
		\resinneritem{Designed an Android application to algorithmically navigate a user past obstacles to a chosen destination on a map using magnetic field and gyroscope sensor inputs.}
	\end{itemize}
	 \vspace{-4pt}
	\resitem{\textbf{Relevant Courses:} Operating Systems, Algorithms \& Data Structures, Embedded Microprocessor Systems, Digital Computers.}
	\resitem{\textbf{Awards}}
	\begin{itemize}
  	\resawardentry{\hspace{5pt} Dean's Honour List}{University of Waterloo}{Mar. 2014}
	\end{itemize}
  \end{resentry}
\end{ressection}

\end{document}